The Impact of Aging Population and Education Attainment on Fertility Rate in US over 1990 to 2020

### 2024-04-03 paper/paper.qmd
update code typo

# Load necessary libraries
library(dplyr)
library(ggplot2)
library(tidyr)
library(car)
library(tidyverse)
library(zoo)
```

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
# Load necessary libraries
library(tidyverse)

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Model Summary of the linear regression model between fertility rate and working age population percentage and tertiary education enrollment rate"
#| warning: false
library(jtools)
summ(model)
```

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
plot(model)
```
\newpage

>>>>

# Load necessary libraries
library(dplyr)
library(ggplot2)
library(jtools)
library(tidyr)
library(car)
library(tidyverse)
library(zoo)
```

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Model Summary of the linear regression model between fertility rate and working age population percentage and tertiary education enrollment rate"
#| warning: false

summ(model)
```

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-model-diag
#| fig-cap: "Model Diagnostic Figures"
plot(model)
```
\newpage
